Meta-analysis of the Interoceptive Accuracy Scale

### 2024-06-07 analysis/study1.qmd
fix missing item
@AnafNeves it should work now - let me know if there are further issues

compare_mods <- function(data) {
  m1 <- lavaan::cfa(m1, data = data)
  m4 <- lavaan::cfa(m4, data = data)
  m5 <- lavaan::cfa(m5, data = data)
  m6 <- lavaan::cfa(m6, data = data)
  m7 <- lavaan::cfa(m7, data = data)

  anova(m1, m4, m5, m6, m7) |>
    parameters::parameters() |>
    mutate(AIC = format(round(AIC, 0), nsmall = 0),
           BIC = format(round(BIC, 0), nsmall = 0),
           Chi2 = format(round(Chi2, 2), nsmall = 2),
           Converged = sapply(list(m1, m4, m5, m6, m7), is_converged))
}

>>>>

compare_mods <- function(data) {

  fit_model <- function(f, data) {
    if(!"Cough" %in% names(data)) {
      f <- str_remove(f, fixed("Cough +"))
    }
    lavaan::cfa(f, data = data)
  }

  cfa1 <- fit_model(m1, data = data)
  cfa4 <- fit_model(m4, data = data)
  cfa5 <- fit_model(m5, data = data)
  cfa6 <- fit_model(m6, data = data)
  cfa7 <- fit_model(m7, data = data)

  anova(cfa1, cfa4, cfa5, cfa6, cfa7) |> 
    parameters::parameters() |>
    mutate(AIC = format(round(AIC, 0), nsmall = 0),
           BIC = format(round(BIC, 0), nsmall = 0),
           Chi2 = format(round(Chi2, 2), nsmall = 2),
           Converged = sapply(list(cfa1, cfa4, cfa5, cfa6, cfa7), is_converged))
}
